Learning to Synthesize Rules for Network Intrusion Detectors

### 2020-02-28 paper/paper.tex
pass on 3.0

%% \Mar{Technically, there are $32 (=2^5)$ subsets for a set
%%   with 5 elements. So, it is important to indicate why Table 3 shows
%%   sooo many plausible rules and that this is is a very simple rule
%%   (for illustration).}

@@

\begin{figure*}[ht]
  \centering
  \includegraphics[trim=0 395 50 0,clip,width=0.65\textwidth]{figs/nids-workflow}
  \caption{The \tname\ workflow.}
  \label{fig:overview}
  \vspace{-2ex}
\end{figure*}

@@

\tname\ works as follows. First, it produces a potentially
overspecified rule that captures the malicious traffic, which is
provided on input in the form of pcap files~\cite{pcap}. In this step,
\tname\ detects options directly from the input messages (see
Section~\ref{sec:rules-and-packets}). More precisely, it produces a
rule containing all possible options satisfied by the traffic. Let us
refer to that rule as the \emph{seed rule} and its corresponding set
of options as \emph{seed options}. Note that, as only malicious
traffic is considered in this step, the seed rule is likely
overspecified, \ie{}, it may be more restrictive than the golden rule
(see Section~\ref{sec:suri-metas-coverage}). Consequently, the use of
that rule to capture attacks associated with the input traffic could
lead to false negatives.  Second, \tname\ generates rules that weaken
the constraints associated with the seed options whilst still
capturing the malicious traffic. Given that every option declared in a
rule needs to be satisfied for a rule to capture an attack, any subset
of the set of seed options must capture the malicious traffic by
definition. \tname{} leverages that observation to search for rules
containing a proper subset of options from the seed options. However,
note that that approach alone could result in false positives as it
imposes no limit on to what extent a rule can be relaxed. \tname{}
uses benign traffic for that purpose. More precisely, it uses a
gradient descent-like search to find all plausible rules derived from
the seed rule, obtained in the previous step. Finally, \tname{} uses
several heuristic functions derived from a data set of existing rules
to rank the plausible rules generated in the previous step by their
similarity to existing rules. The rationale is that many plausible
rules can be generated in this step and they have different semantics,
which can differ from user's intent. Similarity is used to approximate
user's intent.

>>>>

@@

@@

\begin{figure}[h!]
  \centering
  \includegraphics[trim=0 395 50 0,clip,width=0.48\textwidth]{figs/nids-workflow}
  \caption{The \tname\ workflow.}
  \label{fig:overview}
  \vspace{-2ex}
\end{figure}

\tname\ works as follows. First, it produces a rule that captures the
malicious traffic. In this step, \tname\ detects options directly from
the input messages (see Section~\ref{sec:rules-and-packets}). More
precisely, it produces a rule containing all possible options
satisfied by the traffic. Let us refer to that rule as the \emph{seed
  rule} and its corresponding set of options as \emph{seed
  options}. Note that, as only the malicious traffic is considered in
this step, the seed rule is likely overspecified, \ie{}, it may be
more restrictive than the golden rule. Consequently, the use of that
rule could result in false negatives. Second, \tname\ generates
alternative rules that 1) weaken the constraints expressed in the seed
rule while 2) still capturing the malicious traffic. Given that every
option declared in a rule needs to be satisfied for a rule to capture
an attack, any subset of the set of seed options, by definition,
captures the attack characterized by the malicious traffic. \tname{}
leverages that observation to search for rules containing a proper
subset of options from the seed options. However, note that that
approach alone could result in false positives as it imposes no limit
on to what extent a rule can be relaxed. \tname{} uses benign traffic
for that purpose. More precisely, it uses a gradient descent-like
search to find plausible rules derived from the seed rule, obtained in
the previous step. Finally, \tname{} uses several heuristic functions
derived from a data set of existing rules to rank the generated
plausible rules by their similarity with existing rules. Similarity is
used to approximate user's intent.
